Parallel all papers PLS for corn data

### 2019-08-29 MSc Project/Scratch/My_Analysis.Rmd
add the datasets and intro and loop time and sample number

---
title: "Parallel all papers PLS for corn data"
author: "Hongwei Peng"
date: "09/07/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()-1                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")
clusterExport(cl, "rawdata")                           # 额外加载变量
system.time({
  corn_PLS=function(n){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    NV <- 10                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(20:70,300))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSECV",main="PLS")
  boxplot(V3~V1,data=PlotData,xlab="Number of Calibration", ylab="RMSEP",main="PLS")
  PlotDataMean <- apply(PlotData,2,mean)
  PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
})
stopCluster(cl)

```

>>>>

---
title: "Parallel all papers PLS for corn data"
author: "Hongwei Peng"
date: "28/08/2019"
output: html_document
---

#1~m5
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
{
  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
} else {
  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
}
clusterExport(cl, "rawdata")                             # input the rawdata to parallel
clusterExport(cl, "Myriad_flag")
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  #par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of moisture on m5")
  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of moisture on m5")
  #PlotDataMean <- apply(PlotData,2,mean)
  #PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
  if (Myriad_flag==TRUE) {
    save(PlotData,file="1~m5_Number_of_components_PlotData.RData")                  # save results in myriad
  }
  clnum
})
stopCluster(cl)
```

#2~m5
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
{
  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
} else {
  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
}
clusterExport(cl, "rawdata")                             # input the rawdata to parallel
clusterExport(cl, "Myriad_flag")
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  #par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of oil on m5")
  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of oil on m5")
  #PlotDataMean <- apply(PlotData,2,mean)
  #PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
  if (Myriad_flag==TRUE) {
    save(PlotData,file="2~m5_Number_of_components_PlotData.RData")                  # save results in myriad
  }
  clnum
})
stopCluster(cl)
```

#3~m5
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
{
  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
} else {
  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
}
clusterExport(cl, "rawdata")                             # input the rawdata to parallel
clusterExport(cl, "Myriad_flag")
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  #par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of protein on m5")
  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of protein on m5")
  #PlotDataMean <- apply(PlotData,2,mean)
  #PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
  if (Myriad_flag==TRUE) {
    save(PlotData,file="3~m5_Number_of_components_PlotData.RData")                  # save results in myriad
  }
  clnum
})
stopCluster(cl)
```

#4~m5
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
{
  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
} else {
  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
}
clusterExport(cl, "rawdata")                             # input the rawdata to parallel
clusterExport(cl, "Myriad_flag")
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(m5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  #par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of starch on m5")
  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of starch on m5")
  #PlotDataMean <- apply(PlotData,2,mean)
  #PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
  if (Myriad_flag==TRUE) {
    save(PlotData,file="4~m5_Number_of_components_PlotData.RData")                  # save results in myriad
  }
  clnum
})
stopCluster(cl)
```

#1~mp5
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
{
  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
} else {
  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
}
clusterExport(cl, "rawdata")                             # input the rawdata to parallel
clusterExport(cl, "Myriad_flag")
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  #par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of moisture on mp5")
  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of moisture on mp5")
  #PlotDataMean <- apply(PlotData,2,mean)
  #PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
  if (Myriad_flag==TRUE) {
    save(PlotData,file="1~mp5_Number_of_components_PlotData.RData")                  # save results in myriad
  }
  clnum
})
stopCluster(cl)
```

#2~mp5
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
{
  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
} else {
  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
}
clusterExport(cl, "rawdata")                             # input the rawdata to parallel
clusterExport(cl, "Myriad_flag")
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,2])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  #par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of oil on mp5")
  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of oil on mp5")
  #PlotDataMean <- apply(PlotData,2,mean)
  #PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
  if (Myriad_flag==TRUE) {
    save(PlotData,file="2~mp5_Number_of_components_PlotData.RData")                  # save results in myriad
  }
  clnum
})
stopCluster(cl)
```

#3~mp5
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
{
  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
} else {
  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
}
clusterExport(cl, "rawdata")                             # input the rawdata to parallel
clusterExport(cl, "Myriad_flag")
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,3])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  #par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of protein on mp5")
  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of protein on mp5")
  #PlotDataMean <- apply(PlotData,2,mean)
  #PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
  if (Myriad_flag==TRUE) {
    save(PlotData,file="3~mp5_Number_of_components_PlotData.RData")                  # save results in myriad
  }
  clnum
})
stopCluster(cl)
```

#4~mp5
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
{
  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
} else {
  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
}
clusterExport(cl, "rawdata")                             # input the rawdata to parallel
clusterExport(cl, "Myriad_flag")
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp5data),                  #input data
                     y=propvals[,4])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  #par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of starch on mp5")
  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of starch on mp5")
  #PlotDataMean <- apply(PlotData,2,mean)
  #PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
  if (Myriad_flag==TRUE) {
    save(PlotData,file="4~mp5_Number_of_components_PlotData.RData")                  # save results in myriad
  }
  clnum
})
stopCluster(cl)
```

#1~mp6
```{r echo=FALSE,warning=FALSE,message=FALSE}
library(R.matlab)
library(pls) 
library(lars)
library(ggplot2)
library(parallel)                                      # 载入parallel包
clnum<-detectCores()                                 # 计算可用线程数，并设置并行使用线程数
cl <- makeCluster(getOption("cl.cores", clnum))        # 初始化并行
Myriad_flag=TRUE                                        # myriad_flag TRUE means in cluster environment 
if (Myriad_flag==TRUE)                                   # FALSE means in PC environment
{
  rawdata <- readMat("/home/uczlhpe/Scratch/corn.mat")   # Myriad dir
} else {
  rawdata <- readMat("/Users/hongwei/Downloads/corn.mat")# PC dir
}
clusterExport(cl, "rawdata")                             # input the rawdata to parallel
clusterExport(cl, "Myriad_flag")
system.time({
  corn_PLS=function(NV){                                #n is the number of calibration
    library(pls)
    m5data <- rawdata$m5spec$data
    mp5data <- rawdata$mp5spec$data
    mp6data <- rawdata$mp6spec$data
    propvals <- rawdata$propvals$data
    #m5data <- m5data[,c(-75,-77)]
    #propvals <- propvals[,c(-75,-77)]

    n <- 60                                           #number of variables 
    sample <- sample(1:80)                             #set random order; the begin of reset order
    DF <- data.frame(NIR = I(mp6data),                  #input data
                     y=propvals[,1])
    class(DF$NIR) <- "matrix"                          # just to be certain, it was "AsIs"
    #str(DF)                                           #check point
    DF$train <- rep(FALSE, 80)
    DF$train[sample<=n] <- TRUE                        #chose calibration
    corn.pls <- plsr(y ~ NIR, data = DF, ncomp = NV, validation="LOO", jackknife = TRUE, subset = train)
    #summary(corn.pls,what="all")                      #check point
    RMSECV <- RMSEP(corn.pls)$val[1,1,NV]
    #print(RMSECV)                                     #check point
    predict <- predict(corn.pls, ncomp = NV, newdata = DF[!DF$train,])
    RMSEP <- sqrt(sum((predict-DF[!DF$train,]$y)^2)/(80-n))
    #print(RMSEP)                                      #check point
    #plot(R2(corn.pls))                                #check point
    return(cbind(RMSECV,RMSEP))                        #return 1x2matrix
  }
  #corn_PLS(n)
  n <- as.matrix(rep(1:50,50))                           #the number of calibration, rep(a:b,c): from a to b and repeat c. 
  #PlsResult <- apply(n,1,corn_PLS)                     #loop
  PlsResult <- parSapply(cl,n,corn_PLS)                #optimizated loop
  PlotData <- as.data.frame(cbind(n,t(PlsResult)))     #combind the results
  #par(mfrow=c(1,2))
  boxplot(V2~V1,data=PlotData,xlab="Number of components", ylab="RMSECV",main="PLS of moisture on mp6")
  boxplot(V3~V1,data=PlotData,xlab="Number of components", ylab="RMSEP",main="PLS of moisture on mp6")
  #PlotDataMean <- apply(PlotData,2,mean)
  #PlotDataSd <- apply(PlotData,2,sd)
  #cat(PlotDataMean[2]-PlotDataSd[2],PlotDataMean[2],PlotDataMean[2]+PlotDataSd[2],"\n")
  #cat(PlotDataMean[3]-PlotDataSd[3],PlotDataMean[3],PlotDataMean[3]+PlotDataSd[3],"\n")
  if (Myriad_flag==TRUE) {
    save(PlotData,file="1~mp6_Number_of_components_PlotData.RData")                  # save results in myriad
  }
  clnum
})
stopCluster(cl)
```
